Cognate beginnings to bilingual lexical acquisition

### 2023-07-25 docs/index.qmd
Update Dockerfile

@@

    # join
    out <- bind_cols(x_character, x_numeric) |> 
        pivot_longer(everything(),
                     names_to = c("variable", "measure"),
                     values_to = "value",
                     names_sep = "\\.", ) |> 
        pivot_wider(id_cols = variable,
                    names_from = "measure",
                    values_from = "value",
                    values_fn = \(x) ifelse(is.character(x),
                                            paste0(x, collapse = ","),
                                            unlist(x)))

@@

:::

>>>>

    x <- flatten_columns(x)

@@

    # describe date variables
    date.fns <- tibble::lst(nmissing, min, max)
    x_date <- x |> 
        summarise(across(where(is.Date), 
                         date.fns,
                         .names = "{.col}.{.fn}"))

    # join
    out <- bind_cols(x_character, x_numeric, x_date) |> 
        pivot_longer(everything(),
                     names_to = c("variable", "measure"),
                     values_to = "value",
                     names_sep = "\\.", ) |> 
        pivot_wider(id_cols = variable,
                    names_from = "measure",
                    values_from = "value",
                    values_fn = \(x) ifelse(is.character(x),
                                            paste0(x, collapse = ","),
                                            unlist(x))) |> 
        mutate(varclass = purrr::map_chr(x, class)) |> 
        relocate(varclass, .after = variable)

@@

```{r items-dict}
tar_load(items)

items_dict <- data_dict(items) |> 
    mutate(comments = c(
        "Concept associated to the word-form, uniquely identifies every translation equivalent",
        "Language to which the word-form belongs to. Can be Catalan or Spanish",
        "Uniquely identifies the word-form in the questionnare",
        "Phonological transcription of the word-form in the IPA format",
        "Phonological transcription of the word-form in X-SAMPA format",
        "Syllables in the word-form",
        "Questionnaire sub-list in which the word-form appears",
        "Uniquely identifies every translation equivalent",
        "Levenshtein distance between the word-form and its translation",
        "Number of phonemes in the word-form",
        "Number of syllables in the word-form",
        "Lexical frequency in Zipf scores, from the English CHILDES corpora",
        "Sum of the frequency of the syllables in the word-form, expressed as counts per million tokens"
    ))
options(knitr.kable.NA = '--')

kable(items_dict,
      col.names = c(
          "Variable",
          "Type",
          "# missing",
          "# levels",
          "Mean",
          "Median",
          "SD",
          "Min",
          "Max",
          "Description"
      ))
```

## Participants

```{r participants-dict}
tar_load(participants)

participants_dict <- data_dict(participants) |> 
    mutate(comments = c(
        "Concept associated to the word-form, uniquely identifies every translation equivalent",
        "Language to which the word-form belongs to. Can be Catalan or Spanish",
        "Uniquely identifies the word-form in the questionnare",
        "Phonological transcription of the word-form in the IPA format",
        "Phonological transcription of the word-form in X-SAMPA format",
        "Syllables in the word-form",
        "Questionnaire sub-list in which the word-form appears",
        "Uniquely identifies every translation equivalent",
        "Levenshtein distance between the word-form and its translation",
        "Number of phonemes in the word-form",
        "Number of syllables in the word-form",
        "Lexical frequency in Zipf scores, from the English CHILDES corpora",
        "Sum of the frequency of the syllables in the word-form, expressed as counts per million tokens"
    ))
options(knitr.kable.NA = '--')

kable(items_dict,
      col.names = c(
          "Variable",
          "Type",
          "# missing",
          "# levels",
          "Mean",
          "Median",
          "SD",
          "Min",
          "Max",
          "Description"
      ))
:::
